Humann2 bar plot for gene family

### 2020-02-07 scripts/10_genefamilies_KO_regroup.Rmd
udpate

>>>>

```{r}
# look at the KOs that is involved in the secondary bile acid biosynthesis

bile_KOs <- c('K01442','K15868','K15869','K15870','K15871','K15872','K15873','K15874')
bile_KOs <- paste(bile_KOs, collapse = '|')

ko_genef <- read_tsv('../data/humann2_res/humann2_genefamilies_KO_regroup.tsv') %>% 
  filter(str_detect(`# Gene Family`, bile_KOs)) %>% 
  filter(str_detect(`# Gene Family`, '\\|')) %>% 
  distinct(`# Gene Family`) %>% 
  rename(genefam = `# Gene Family`) %>% 
  separate(genefam, into = c('KO_ID','species') ,sep = '\\|'  )
